---
title: "General Information"
---

## Date and location

The school will be held from **15 to 19 September 2025** at the **Institute of Archaeology, Czech Academy of Sciences, Brno** ([https://arub.cz/](https://arub.cz/){.external}) at the address given below:

> Čechyňská 363/19  
> 602 00 Brno  
> Czech Republic

::: {.callout-tip}

## Note

Please note that this is an on-site event only, and remote participation will **not** be possible.
:::

```{r}
#| echo: false
#| warning: false
library(leaflet)

# ARUB location
arub <- c(16.6208208, 49.1892306)
popup <- paste0("<a href=https://maps.app.goo.gl/puXXYwHgCfgB8Lg9A target=_external>Google Maps</a>")

# places for lunches
m <- read.csv("meals.csv") %>% 
  dplyr::mutate(popup = paste0("<b>", place, "</b><br>", 
                        cuisine, "<br>",
                        "<i>", note, "</i>"))

# map
leaflet() %>% 
  addTiles() %>% 
  setView(lng = arub[1], lat = arub[2], zoom = 15) %>% 
  addMarkers(lng = arub[1], lat = arub[2], popup = popup) %>% 
  addCircleMarkers(lng = m$lng, lat = m$lat, popup = m$popup, 
                   stroke = "", fillOpacity = 0.4)
```


## Grants

Each participant of the school is eligible to receive a grant to cover travel expenses, housing, and daily subsistence during the meeting. 
To receive the grant, participants need to:

1. **Apply via the official form** of the ATRIUM Project (see the [Applications](applications.qmd) section for details).
2. **Participate in person**, i.e. sign attendance sheets for each training day.
3. **Submit a report** within a given time frame after the conclusion of the school with details of their participation. *Please note that the grant will be disbursed only upon the successful submission of this report*.


## Prerequisites

- **Bring your own laptop!**
- Bring a **camera** (or a phone with a good camera) you feel comfortable with.
    - When choosing from multiple lenses, wide-angle lenses are generally more suitable for the documentation of historic monuments. For artefact documentation, standard lenses (with a focal length around 50mm) are recommended.
- **Install** [**RealityScan**](https://www.realityscan.com/en-US/download), a free 3D photogrammetry software.

*Note: RealityScan **requires** a Windows computer with CUDA-enabled NVIDIA graphics card. If your system does not meet these requirements, you can download and install alternative software solutions. The most user-friendly alternative is [3DF Zephyr Free](https://www.3dflow.net/3df-zephyr-free/), which supports importing a maximum of 50 photos only. Another alternative (significantly slower and less user-friendly) is [MeshroomCL](https://github.com/openphotogrammetry/meshroomcl).*

## Other information

### Travelling to Brno

Brno is easily reachable by trains or buses from Prague (approx. a 2 to 2.5-hour journey) and Vienna (approx. a 1.5 to 2-hour journey). 
Many overnight trains crossing a large part of Europe start or end in Vienna, and we recommend taking these trains as an alternative to flying.

### Accommodation

No accommodation is provided to participants. Please arrange your accommodation in one of many cities hotels or hostels.
<!-- We will add some tips for places close to the venue. -->

### Food

There are several places around the institute, see map above for locations. 

```{r}
#| echo: false
read.csv("meals.csv") %>% 
  dplyr::select(-lng, -lat) %>% 
  dplyr::arrange(cuisine) %>% 
  knitr::kable()
```
